\thesistitle

### 2019-08-22 sections/research.tex
Good enough

\begin{align*}\label{eq:typerelation}
%N_{1R} = \{n | n = a node found using the T1R set of rules\}
%N_{2R} = \{n | n = a node found using the T2R set of rules\}
%N_{3R} = \{n | n = a node found using the T3R set of rules\}
\centerline{\text{$N_{T1R} \subseteq N_{T2R} \subseteq N_{T3R}}$} \\
\text{where}~N_{T1R} &= \text{\{n | n = a node found using the T1R set of rules\}} \\
  N_{T2R} &= \text{\{n | n = a node found using the T2R set of rules\}} \\
	N_{T3R} &= \text{\{n | n = a node found using the T3R set of rules\}}
\end{align*}

Comparing these clone type definitions to the ones used in literature, type 1R clones are a subset of type 1 clones. However, this subset relation does not exist for type 2R and 3R clones. This is because these definitions allow variability in multi-token method calls, which type 2 and type 3 do not allow. Because of that, the following is true for these clone types:

\begin{equation}\label{eq:typerelation2}
N_{T1R} \subseteq N_{T1} \text{, but } N_{T2R} \nsubseteq N_{T2} \text{ and } N_{T3R} \nsubseteq N_{T3}
\text{where}~N_{T1} &= \text{\{n | n = a node found using the T1 set of rules\}} \\
  N_{T2} &= \text{\{n | n = a node found using the T2 set of rules\}} \\
	N_{T3} &= \text{\{n | n = a node found using the T3 set of rules\}}
\end{equation}

>>>>

\begin{equation}\label{eq:typerelation}
%N_{1R} = \{n | n = a node found using the T1R set of rules\}
%N_{2R} = \{n | n = a node found using the T2R set of rules\}
%N_{3R} = \{n | n = a node found using the T3R set of rules\}
N_{T1R} \subseteq N_{T2R} \subseteq N_{T3R}
\end{equation}

Where $N_{\text{clone type}}$ is the set of cloned nodes found by the rules of the specified clone type. Comparing these clone type definitions to the ones used in literature, type 1R clones are a subset of type 1 clones. However, this subset relation does not exist for type 2R and 3R clones. This is because these definitions allow variability in multi-token method calls, which type 2 and type 3 do not allow. Because of that, the following is true for these clone types:

\begin{equation}\label{eq:typerelation2}
N_{T1R} \subseteq N_{T1} \text{, but } N_{T2R} \nsubseteq N_{T2} \text{ and } N_{T3R} \nsubseteq N_{T3}
\end{equation}

Where $N_{\text{clone type}}$ is the set of cloned nodes found by the rules of the specified clone type.
